Figures

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
cdl demo works

```{r cdl_viewport}
library(raster)
library(dplyr)

@@

@@

test2 <- cdl_table %>% 
  dplyr::filter(description != "Background") %>%
  rename(n = Freq) %>%
  arrange(desc(n)) %>%
  group_by(category) %>%
  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
  ungroup() %>%
  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
  dplyr::filter(percent >= 1) %>%
  arrange(is_ag, percent) 
%>%
  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)

test2 <- test2 %>%
  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
            sum(dplyr::filter(test2, is_ag == "ag" & 
                                category != "pasture")$percent))

>>>>

```{r cdl_viewport}
library(raster)
library(dplyr)
library(stars)

@@

cdl_df <- as.data.frame(r, xy = TRUE) %>%
  dplyr::select(x, y, contains("2745"))
names(cdl_df)[3] <- "value"
cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code"))

ggplot() + 
  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category))

@@

test2 <- cdl_table %>% 
  dplyr::filter(description != "Background") %>%
  rename(n = Freq) %>%
  arrange(desc(n)) %>%
  group_by(category) %>%
  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
  ungroup() %>%
  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
  dplyr::filter(percent >= 1) %>%
  arrange(is_ag, percent)

test2 <- test2 %>%
  add_row(category = "crops", group_n = NA, is_ag = NA, percent = 
            sum(dplyr::filter(test2, is_ag == "ag" & 
                                category != "pasture")$percent))
